Verifying Demonstrations

### 2017-11-16 contents-poster.tex
Adds whiteblock and changes blocks, edits middle column

    \begin{blackblock}{Designated protest}
      \begin{itemize}
        \item A protest is identified by its cause, captured in a 
          manifesto.
        \item The hash of the manifesto provides an unpredictable identifier 
          (\(cid\) in figures).
        \item It's difficult to create a second manifesto that disagrees but 
          gets the same identifier.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Privacy-preserving linkability}
      \begin{itemize}
        \item We want linkability to prevent Sybil attacks.
        \item We also want privacy.
        \item We use techniques from anonymous credentials to create identifiers 
          (\(pid, wid\) in figures).
        \item The identifiers are random but unique per protest, i.e.\ depends 
          on \(cid\).
        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
          verification).
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Temporal eligibility}
      \begin{itemize}
        \item We use a blockchain for commitments, freshness.
        \item Freshness: a protester must include the head (hash value) of the 
          blockchain in their proof shares (\(t_s\) in figures).
        \item This value is difficult to guess and prevents preparing proofs too 
          long in advance.
        \item Commitments: when a proof share is prepared, it is committed to 
          the blockchain for timestamping.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Location proofs and spatial eligibility}
      \begin{itemize}
        \item Each proof must be bound to the location.
        \item This is done using witnesses.
        \item A witness runs a distance-bounding protocol to ensure proximity.
        \item If in proximity, the witness will issue a witness identifier and 
          signature (\(wid, wsig\)).
      \end{itemize}
    \end{blackblock}

    \begin{blueblock}{Verifying the participation count}
      \begin{enumerate}
        \item We must verify the eligibility of each proof, i.e.\ of all its 
          shares.
        \item We must count these valid proofs.
        \item Each protester must check that their proof is indeed registered so 
          that it can be counted.
      \end{enumerate}
    \end{blueblock}

\begin{blackblock}{Eligibility and universal verifiability}

Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.
We note that these proofs are not needed until the verification step after the 
protest.
Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
above) whereas their respective \ac{NIZK} proof can be computed and published 
after the protest.

Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
witness knows a signature by the identity authority on \(k_W\).
With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
eligibility, of the proof shares and thus also count them.

\end{blackblock}

\begin{blackblock}{Individual verifiability and receipt freeness}

The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
an adversary from dropping participation proofs.
Thus each protester must verify that their own proof is indeed included.
This can be accomplished as follows.
After Alice commited to her proof (share) in the blockchain, she stores the hash 
of the block.
At a later time, she can still verify that the block is indeed still there.
At this point, this hash value is the only thing she must store for individual 
verifiability.

More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
must remove her secret PRF key, \(k_A\).
With this key Eve can verify that Alice has submitted a proof by computing 
\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).

\end{blackblock}

>>>>

    \begin{greenblock}{Our approach: during protest}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
          placard).
        \item Each protester scans the QR code, computes a protest (cause) 
          identifier (\(cid\)) to designate their participation.
        \item Each protester computes a personal identifier (\(pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (unlinkable between protesters) for 
          other protesters by creating participation-proof shares.
        \item Proof shares vouches for temporal and spatial eligibility.
      \end{itemize}
    \end{greenblock}

    \begin{whiteblock}{Designated protest}
      \begin{itemize}
        \item A protest is identified by its cause, captured in a 
          manifesto.
        \item The hash of the manifesto provides an unpredictable identifier 
          (\(cid\) in figures).
        \item It's difficult to create a second manifesto that disagrees but 
          gets the same identifier.
      \end{itemize}
    \end{whiteblock}

    \begin{whiteblock}{Privacy-preserving linkability}
      \begin{itemize}
        \item Need linkability during a protest to prevent Sybil attacks.
        \item Also need privacy.
        \item Uses techniques from anonymous credentials to create identifiers 
          (\(pid, wid\) in figures).
        \item The identifiers are random but unique per protest, i.e.\ depends 
          on \(cid\).
        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
          verification).
      \end{itemize}
    \end{whiteblock}

    \begin{whiteblock}{Temporal eligibility}
      \begin{itemize}
        \item We use a blockchain for commitments, freshness.
        \item Freshness: a protester must include the head (hash value) of the 
          blockchain in their proof shares (\(t_s\) in figures).
        \item This value is difficult to guess and prevents preparing proofs too 
          long in advance.
        \item Commitments: when a proof share is prepared, it is committed to 
          the blockchain for timestamping.
      \end{itemize}
    \end{whiteblock}

    \begin{whiteblock}{Location proofs and spatial eligibility}
      \begin{itemize}
        \item Each proof must be bound to the location.
        \item This is done using witnesses.
        \item A witness runs a distance-bounding protocol to ensure proximity.
        \item If in proximity, the witness will issue a witness identifier and 
          signature (\(wid, wsig\)).
      \end{itemize}
    \end{whiteblock}

    \begin{greenblock}{Our approach: after the protest}
      \begin{itemize}
        \item Proof shares are committed to a blockchain as soon as possible.
        \item \ac{NIZK} proofs are submitted whenever convenient.
        \item Anyone can verify the proofs: eligibility, universal and 
          individual verifiability.
        \item Must be done for all shares and their \ac{NIZK} proofs.
        \item Count all \(pid\)s with valid proofs.
      \end{itemize}
    \end{greenblock}

    \begin{whiteblock}{Eligibility and universal verifiability}
      \begin{itemize}
        \item Verify that \(pid\), \(wid\) and \(wsig\) are correct, i.e.\ verify 
          their \ac{NIZK} proofs.
        \item \ac{NIZK} proofs must show \(pid = PRF_{k_P}(id)\) and \(k_P\) is 
          signed by \iac{CA}.
        \item \ac{NIZK} proofs must show \(wid = PRF_{k_W}(pid), wsig = 
            PRF_{k_W}(wid, t_s, l)\) and \(k_W\) is signed by \iac{CA}.
      \end{itemize}
    \end{whiteblock}

    \begin{whiteblock}{Individual verifiability and receipt freeness}
      \begin{itemize}
        \item Each protester can verify that their proof is available on the 
          blockchain.
        \item Protester no longer needs to keep the proof, just the hash.
        \item Eve can use \(k_P\) to redo the computations to verify 
          participation:
          \[pid'\gets PRF_{k_A}(cid) \text{ and compare } pid = pid'.\]
        \item However, requires arrest.
      \end{itemize}
    \end{whiteblock}
